---
title: "County Department Finances FY 2023/24"
description: "Controller of Budget data on county departmental budgets, exchequer releases and expenditure"
format: pdf
---

```{r setup, include=FALSE}
library(dplyr)
library(knitr)
library(scales)

data <- read.csv("../data/county-finances-sep2024.csv")
```

## Dataset Overview

This documentation describes county financial data from Kenya's Controller of Budget for FY 2023/24 by departments.

### Key Information
```{r key-info, echo=FALSE}
info <- list(
  "Size" = "74KB",
  "Records" = nrow(data),
  "Time Period" = "2023-2024"
)

data.frame(
  Value = unlist(info)
) |> 
  kable()
```

## Data Dictionary

```{r dictionary, echo=FALSE}
dictionary <- tibble(
  Variable = c(
    "department", "budget_rec", "budget_dev", "exch_rec", "exch_dev",
    "exp_rec", "exp_dev", "exp_exch_rec", "exp_exch_dev", "abs_rec",
    "abs_dev", "county"
  ),
  Description = c(
    "Department name",
    "Recurrent budget allocation (Million KES)",
    "Development budget allocation (Million KES)",
    "Recurrent exchequer releases (Million KES)",
    "Development exchequer releases (Million KES)",
    "Recurrent expenditure (Million KES)",
    "Development expenditure (Million KES)",
    "Recurrent expenditure as % of exchequer",
    "Development expenditure as % of exchequer",
    "Recurrent absorption rate (%)",
    "Development absorption rate (%)",
    "County name"
  ),
  Type = c(
    "Character", rep("Numeric", 10), "Character"
  )
)

kable(dictionary)
```

## Data Quality Notes

The analysis in this document uses data from the Controller of Budget's reports.  
My cleaning and scraping script is available at [Github](https://github.com/Tagnal-hub/data)


### Data Source
Original data: [Controller of Budget Reports](https://cob.go.ke/reports/consolidated-county-budget-implementation-review-reports/)

### Files
- Source data: [CSV file](/data/county-finances-sep2024.csv)
- Documentation: [PDF documentation](/docs/county-finances-sep24.pdf)

### Attribution
This analysis uses data from the Controller of Budget, Kenya. 